An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-12-31 EconGrowth2.Rnw
Changed name of loadCESResampleTrianglePlotData to loadCESResampleData

>>>>

<<CES_lambda_gamma_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\lambda$ and $\\sigma$ values for CES resample models.">>=
cesQResampleData <- loadCESResampleData(nest="all", energyType="Q")
# standardScatterPlot(data=data, mapping=aes(gamma_coef, lambda, colour=isConv), facet_formula=countryAbbrev~nest)
standardScatterPlot(data=cesQResampleData, mapping=aes(gamma_coef, lambda), facet_formula=countryAbbrev~nest, alpha=0.1)
@
